\addcontentsline{toc}{chapter}{List of publications}

\chapter*{List of publications}

\section*{International Journals}
\subsection*{Ongoing review as main author}
\begin{itemize}
    \item Febvre, Q., Sommer, J. L., Ubelmann, C., \& Fablet, R. (2023, September 19). Training neural mapping schemes for satellite altimetry with simulation data. arXiv. https://doi.org/10.48550/arXiv.2309.14350 (Submitted at Journal of Advances in Modelling Earth Systems) 
    \item Febvre, Q., Ubelmann, C., Sommer, J. L., \& Fablet, R. (2023). Scale-aware neural calibration for wide swath altimetry observations. ArXiv, abs/2302.04497. (Submitted at IEEE Transactions on Geoscience and Remote Sensing) 
\end{itemize}

\subsection*{Accepted as contributor}
\begin{itemize}
    \item Fablet, R., Febvre, Q., \& Chapron, B. (2023). Multimodal 4DVarNets for the Reconstruction of Sea Surface Dynamics From SST-SSH Synergies. IEEE Transactions on Geoscience and Remote Sensing, 61, 1–14. https://doi.org/10.1109/TGRS.2023.3268006
    \item Beauchamp, M., Febvre, Q., Georgenthum, H., \& Fablet, R. (2023). 4DVarNet-SSH: end-to-end learning of variational interpolation schemes for nadir and wide-swath satellite altimetry. Geoscientific Model Development, 16(8), 2119–2147. https://doi.org/10.5194/gmd-16-2119-2023
    \item Beauchamp, M., Febvre, Q., Georgentum, H., \& Fablet, R. (2022). 4DVarNet-SSH: end-to-end learning of variational interpolation schemes for nadir and wide-swath satellite altimetry. Geoscientific Model Development.
    \item Fablet, R., Amar, M. M., Febvre, Q., Beauchamp, M., \& Chapron, B. (2021). END-TO-END PHYSICS-INFORMED REPRESENTATION LEARNING FOR SATELLITE OCEAN REMOTE SENSING DATA: APPLICATIONS TO SATELLITE ALTIMETRY AND SEA SURFACE CURRENTS. ISPRS Annals of the Photogrammetry, Remote Sensing and Spatial Information Sciences, V-3–2021, 295–302. https://doi.org/10.5194/isprs-annals-V-3-2021-295-2021
\end{itemize}

\section*{International Conferences}
\subsection*{Accepted as first author or co-author}
\begin{itemize}
    \item Johnson, J. E., Febvre, Q., Gorbunova, A., Metref, S., Ballarotta, M., Sommer, J. L., \& Fablet, R. (2023, September 27). OceanBench: The Sea Surface Height Edition. arXiv. https://doi.org/10.48550/arXiv.2309.15599 (Accepted at NEURIPS 2023)
    \item Febvre, Q., Fablet, R., Sommer, J. L., \& Ubelmann, C. (2022). Joint calibration and mapping of satellite altimetry data using trainable variational models. In ICASSP 2022 - 2022 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP) (pp. 1536–1540). https://doi.org/10.1109/ICASSP43922.2022.9746889
\end{itemize}



% \begin{bibunit}[IEEEtran.bst]
% \renewcommand\bibname{List of publications}
% \nocite{*}
% \putbib[./PublicationList/PubList-Biblio.bib]
% \end{bibunit}



